Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-09-21 publication/manuscript.Rmd
remove performance measure formulas

Throughout our experiments, we use 5-fold CV to obtain estimates of predictive performance.
Depending on the target variable, we report root mean squared error (RMSE) for regression, area under the curve (AUC) for binary classification, and its extension AUNU [@ferri_2009] for multiclass problems:
\begin{align*}
RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^N(y_i-\hat{y_i})^2},\
AUC = \frac{U}{N_{pos} \cdot N_{neg}},\
AUNU = \frac{\sum_{c = 1}^C AUC_c}{C}
\end{align*}
$N$: number of observations, $N_{pos}$ and $N_{neg}$: number of true labels in both classes, $U$: test statistic of the Mann-Whitney-U test, and $AUC_c$: one vs. rest $AUC$ of class $c$.

>>>>

Throughout our experiments, we use 5-fold CV to obtain estimates of predictive performance.
Depending on the target variable, we report root mean squared error (RMSE) for regression, area under the curve (AUC) for binary classification, and its extension AUNU [@ferri_2009] for multiclass problems.
